User-level Grid Monitoring with Inca 2

### 2007-02-25 pubs/papers/hpdc-gmw-2007/paper.tex
additions to arch section
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6553 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

% Uncomment to check text length -- moves figures to end of paper -- no more
% than 10 % pages w/o figures
%\usepackage{endfloat}

@@

\SubSection{Inca administration GUI tool (incat)}

The Inca administrative GUI tool (incat) is the main interface by which an
Inca administrator interacts with the Inca system.  Incat allows the Inca
administrator to view the choose which resources to monitor and which tests or 
benchmarks to deploy to those resources.  The following subsections
describe the Inca components that are configurable via incat.  
To configure reporter execution, an Inca administrator launches a GUI tool,
called incat.  Incat allows the administrator to choose which resources to
monitor and which reporters to deploy to those resources.  For each
reporter, the administrator can specify the resources to run on,
command-line arguments, the runtime environment, the frequency of execution,
and resource limits. The Inca administrator may also group related reporters
into suites that can be shared across different Inca deployments.  This can
be useful to determine interoperability among Grids or to determine whether
an application's requirements are being fulfilled on a Grid.

\subsubsection{Suites}
%\subsubsection{Series}

\subsubsection{Resource Macros}

@@

The Inca agent is a server that implements the configuration specified by the
Inca administrator.  After determining which Inca tests should be executed on
each resource, the agent stores this configuration information in the depot.
It then stages and launches a dependent component, called a reporter manager,
on each resource using either SSH or Globus [13].  Once a reporter manager
contacts its agent, the agent transmits Inca tests to execute, along with
their dependencies, configuration and schedule of execution.

@@

The Inca reporter manager is a lightweight process responsible for managing
the schedule and execution of Inca tests, called reporters, on a single
resource. The reporter manager receives reporter updates and dependencies
(e.g., Inca Perl APIs or source code) from the agent along with requests for
reporter scheduling changes.  Running under a regular user account, the
reporter manager executes reporters on-demand or using an internal cron
scheduler, and sends reports to the depot for archiving. The reporter
manager monitors reporter system usage and enforces limits (e.g., wall clock
time, CPU time, memory).  System usage information is sent to the depot with
each report.

@@

The Inca depot server is responsible for storing configuration information
and the data produced by reporters. The depot maintains a relational
database via Hibernate [14] so that it can use a variety of databases.  The
depot provides full archiving of reporter output and structures its schema
to reduce redundant data.  Data can be queried using SQL queries. Predefined
queries exist to return the latest report instances of a suite, a single
report instance, or a report history.  A Web services interface is also
available to provide unauthenticated query access to data.

@@

The Inca data consumer is a Web application that queries the Inca depot for
data and displays it in a user-friendly format.  The data consumer is
packaged with Jetty [15] so that pages can be served immediately without
deploying Tomcat [16].  A set of JSP tags and pages query the Inca depot for
data (returned as XML) and a set of XSL stylesheets format the data as HTML.

~\newpage
~\newpage
~\newpage
~\newpage
%-------------------------------------------------------------------------

@@

TeraGrid's Inca 2 agent, depot and consumer components are hosted at SDSC on 
sapa.sdsc.edu.  A reporter repository for TeraGrid is also hosted
at SDSC on login-linux.sdsc.edu.  TeraGrid's 19 compute resources
each run a reporter manager and regularly execute an average of 109 reporters
to perform 48 cross-site, 20 grid, 28 cluster, 9 data, 2 user tool, and 2
security tests.  Figure~\ref{tg_deploy_fig} illustrates TeraGrid's Inca 2 
deployment configuration.

>>>>

@@

\SubSection{Inca administration tool (incat)}
%\begin{figure}[htb]
%  \centering
%  \mbox{\epsfig{file=incat.eps, width=\columnwidth}}
%  \caption{\label{arch_fig} Incat .}
%\end{figure}

% Incat is interface Inca admin uses to configure reporters to resources
% introduce series here; why suites are important It is designed to make the
% effort of configuring and maintaining 100s series on resources easilty
The Inca administrative tool (incat) is a GUI implemented in Java Swing an
Inca administrator uses to configure user-level Grid monitoring on their
resources.  Incat allows an Inca administrator to choose which resources to
monitor and which reporters to deploy to those resources.  The configuration
is stored in a XML file and sent to the agent which handles the implementation
(as described in the next section).  The Inca administrator can reload the
configuration at any point and make updates.  Incat provides a number of
conveniences that enable a large number of results to be managed and collected
with a minimum effort.

Once an Inca administrator enters the location of one more reporter
repositories, incat will load and display the reporters available from them.
For each reporter, the Inca administrator can specify the resources to run on,
input arguments, the runtime environment, the frequency of execution, resource
limits, and email notifications.  The reports that a reporter produces on a
resource when executed with specific set of input arguments and runtime
environment are known as a \emph{report series} (or \emph{series} for short).
Thus, the grid.globus.gramPing reporter in Figure~\ref{pingReporter} would
produce one report series when executed with host tg-login.sdsc.edu and
another report series when executed with dslogin.sdsc.edu.  A set of related
series can be grouped into \emph{suites} and shared across other Inca
deployments.  For example, there could be a Globus suite or a data transfer
performance suite.  Suites can also be useful to determine interoperability
among Grids or to determine whether an application's requirements are being
fulfilled on a Grid.

% Resource information organized to make it easier to maintain
For each monitored resource, an Inca administrator selects an access method
(SSH or Globus) to access the resource and start monitoring there (described
in Sections~\ref{agent} and ~\ref{rm}).  Resources can also be grouped
together and referenced in the series configuration.  This facilitates the
process of executing the same series on multiple resources.  Furthermore,
attributes called \emph{macros} can be attached to resources and resource
groups and similarly be referenced in the series configuration (i.e., inputs
and runtime environment).  For example, it is useful to have a macro called
'jobmanager' since the batch system is likely to differ from one machine to
the next.  A resource macro can also have multiple values in which case the
series will be executed on the resource once for each macro value.  The
benefit of resource groups and macros is that when a reporter is executed on a
resource multiple times with different input arguments, it can be represented
succintly.  Similarly, when a resource attribute is changed, it only has to be
changed in one place and then every series that references it will be updated
as well.  This makes the initial configuration and maintenance easier on the
Inca administrator and less error prone.

@@

The Inca agent is a server that implements the configuration specified by the
Inca administrator.  When it receives a configuration file from the Inca
administrator, it will determine which reporters should be executed on each
resource by expanding the resource macros and groups; it then stores the
expanded configuration information in the depot.  The agent stages and
launches an Inca component, called a reporter manager (described in the
following subsection), on each resource using either SSH or Globus.  Once a
reporter manager contacts its agent, the agent transmits the reporters to
execute along with their dependencies and a suite that contains their series
configuration and schedule of execution.  As an Inca administrator makes
updates to the configuration, the agent will push out new reporters and/or
suite changes to each of the effected resources.

To maintain the Inca deployment, the agent regularly pings the reporter
managers on each resource in order to detect when a reporter manager has
failed so it can be restarted.  For example, if a resource goes down for a
planned maintenance, the agent will attempt to restart the reporter manager
(by default every hour) until it succeeds.  The agent also maintains a local
cache of reporters and their dependencies; it periodically checks the
repositories for updates every 4 hours by default and automatically
distributes them to the reporter managers (if the latest version is desired).  
The agent is implemented in Java.

% myproxy

@@

The Inca reporter manager is a lightweight process responsible for managing
the schedule and execution of Inca reporters on a single resource. The
reporter manager receives reporter updates and dependencies from the agent
along with requests for reporter scheduling changes.  Running under a regular
user account, the reporter manager executes reporters on-demand or using an
internal cron scheduler, and sends reports to the depot for archiving. The
reporter manager monitors reporter system usage using the system command
\texttt{ps} and enforces limits (e.g., wall clock time, CPU time, memory).
System usage information is sent to the depot with each report.

The reporter manager is implemented in Perl since it is available by default
on UNIX machines.  The cron scheduling is implemented using the CPAN perl
module Schedule::Cron.

@@

The Inca depot server is responsible for storing configuration information and
the data produced by reporters. The depot uses a relational database via
Hibernate~\cite{hibernate} so that it can use a variety of databases.  The
depot provides full archiving of reporter output and structures its schema
around series and the minimization of redundant data, i.e., only stores
changes from one report to another in a report series.  The depot also
supports comparisons which are executed on a newly received report; 
currently regular expression matching and version comparisons are 
supported.  Optionally, an Inca administrator can select to receive
email notification when the result of the comparison changes.

Data can be queried using SQL queries. Predefined queries exist to return the
latest report instances of a suite, a single report instance, or a report
history.  A Web services interface is also available to provide
unauthenticated query access to data.  The depot is implemented in Java.

@@

The Inca data consumer is a Web application that queries the Inca depot for
data and displays it in a user-friendly format.  The data consumer is packaged
with Jetty~\cite{jetty} so that pages can be served out of the box.  A set of
extensible JSP tags and pages query the Inca depot for data (returned as XML)
and a set of XSL stylesheets format the data as HTML.  An Inca administrator
can customize the data display by either modifying the XSL stylesheets or
writing their own JSP tags and pages.

\SubSection{Security}

To reduce the security risk of Inca, all Inca components communicate with each
other using SSL by default.  Also, sensitive information such as passwords are
encrypted before being stored to disk on the agent.  To handle reporters that
require a valid proxy credential to execute, the reporter manager will fetch a
short-term proxy from a MyProxy~\cite{myproxy} server (as specified by an Inca
administrator) and then destroys the proxy once the reporter has completed.
The goal is to only have short-term proxies on the machine for the times at
which they are neeed; this is more secure than maintaining a long-term
credential on the resource and easier to manage.  Furthermore, the MyProxy
authentication information is fetched from the agent each time a proxy
credential is needed and then cleared from memory.

\SubSection{Scalability}

~\newpage
%-------------------------------------------------------------------------

@@

TeraGrid's Inca 2 agent, depot and consumer components are hosted at SDSC on 
sapa.sdsc.edu.  A reporter repository for TeraGrid is also hosted
at SDSC on inca.sdsc.edu.  TeraGrid's 19 compute resources
each run a reporter manager and regularly execute an average of 109 reporters
to perform 48 cross-site, 20 grid, 28 cluster, 9 data, 2 user tool, and 2
security tests.  Figure~\ref{tg_deploy_fig} illustrates TeraGrid's Inca 2 
deployment configuration.
